\sys: Property-Guided Program Regeneration\\{\vspace{1em}\large Technical University of Denmark, MSc Thesis {\\\vspace{-1em}} Advisors: Christian Gram Kahlauge and Nikos Vasilakis

### 2025-07-31 docs/paper/draft.tex
Add plugins paragraph
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

>>>>

\heading{Plugins}
In order to maximize the applicability of the \sys framework 
towards many different kinds of transformations,
it is designed as an extensible platform rather than a monolithic tool.
All core functionality is provided by plugins, each contributing
the following functionality in the form three runtime hooks:
(1) \ttt{apply} which obtains static or dynamic properties from the original program (\eg
input-output traces, type signatures, or side-effect summaries),
(2) \ttt{verify} that will check the regenerated program against these properties (re-extracting them and comparing them to the original ones),
and
(3) \ttt{know} facts to the knowledge-base that inform regeneration planning.
